%-------------------------
% Resume in Latex
% Author : Ali Mahdavifar
% Main author : Shubhi Rani
% License : MIT
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[super]{nth}
\usepackage{multicol}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


\hypersetup{colorlinks=false,pdfborderstyle={/S/U/W 0},pdfborder=0 0 1}


%-------------------------
% Custom commands
\newcommand{\Href}[2]{\href{#1}{\underline{#2}}}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    #1 {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubItemDouble}[4]{
\vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
%      \resumeItem{#1}{#2} & \resumeItem{#3}{#4} \\
	\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
  &
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }\\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Ali Mahdavifar}}\\
  \\
  Dept. of Computer Engineering & Email : \Href{mailto:ali.mahdavifar@sharif.edu}{ali.mahdavifar@sharif.edu}\\
  Sharif University of Technology & Mobile : +98 913-054-2242\\
  Azadi Ave, Tehran, Iran\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sharif University of Technology}{Tehran, Iran}
      {B.Sc. in Computer Engineering;  Cumulative GPA: 19.11/20 (Ranked \nth{35} out of 199)}{Sept 2019 - Present}
	    
    \resumeSubheading
      {Shahid Beheshti High School of Kashan (NODET)}{Kashan, Iran}
      {Diploma in Mathematics \& Physics;  Cumulative GPA: 19.81/20}{Sept 2016 - Sept 2019}
      
	   {\scriptsize {Under the supervision of National Organization for Development of Exceptional Talents}}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Max Planck Institute for Informatics (D1: Algorithms and Complexity)}{Saarbrücken, Germany}
    {Summer Intern}{Jul 2022 -  Sept 2022}
    
    \resumeItemListStart
    \resumeItemWithoutTitle
    {Under the supervision of Prof. A. Karrenbauer, I continued a project on the complexity of fine-tuning bias terms in specific neural networks. This summer we succeeded in improving the reductions from a geometrical problem to achieve NP-hardness proof of the problem. Currently, we are working on writing of the paper.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Awards-----------------
\section{Honors and Awards}
	\resumeSubHeadingListStart
		
		\resumeItemWithoutTitle
		{Awarded \textbf{Bronze Medal} in INOI (\textbf{Iran National Olympiad in Informatics)} (Aug 2018).

\Href{https://ioinformatics.org/journal/v11si_2017_25_33.pdf}{INOI} is the national round of IOI, organized by Young Scholars’ Club in Iran.}

  		\resumeItemWithoutTitle
  		{\textbf{Ranked} \nth{36} in \textbf{nationwide universities entrance exam} for B.Sc. programs in
\textit{Mathematics \& Physics} branch, among more than 164,000 participants. (Aug 2019)}

  		\resumeItemWithoutTitle
  		{\textbf{Ranked} \nth{124} in \textbf{nationwide universities entrance exam} for B.Sc. programs in \textit{foreign languages (English)} branch, among more than 165,000 participants. (Aug 2019)}

  		\resumeItemWithoutTitle
  		{Acknowledged as the \textbf{youngest [honorary] member of the academic community of University of Kashan}, actively participating in basic courses of the faculty of mathematics at the age of 12. (Feb 2014) [\Href{https://kashanu.ac.ir/fa/news/2934}{link to the university bulletin}]}

	\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{C/C++ (fluent), Python (fluent), Java (familiar), Verilog (familiar), R (familiar).}
	\resumeSubItem{Database}{SQL databases, specially PostgreSQL.}
\resumeSubHeadingListEnd

%-----------Grades-----------------
\section{Notable Grades}

	\vspace{-10pt}\begin{multicols}{2}
	\resumeSubHeadingListStart
	
		\resumeSubItem{General Maths (1\&2)}{19.5/20.0 \& 19.0/20.0}
		\resumeSubItem{Differential Equations}{18.2/20.0}
		\resumeSubItem{Numerical Computation}{19.5/20.0}
		\resumeSubItem{Computer Simulation}{20.0/20.0}
		\resumeSubItem{Advanced Programming}{20.0/20.0}
		\resumeSubItem{Data structure \& Algorithms}{20.0/20.0}
		\resumeSubItem{Design of Algorithms}{20.0/20.0}
		\resumeSubItem{Linear Algebra}{17.0/20.0}

	\resumeSubHeadingListEnd
	\end{multicols}

%-----------TAs-----------------
\section{Teaching Assistant}

  \resumeSubHeadingListStart
    \resumeSubheading
      {Discrete Mathematics}{Instructor: \Href{http://sharif.edu/~zarrabi/}{Prof. H. Zarrabi-Zadeh}}
      {Responsible for designing some assignments and conducting TA classes and marking tests.}{Spring 2021 \& 2022 \& 2023}

    \resumeSubheading
      {Data Structures and Algorithms}{Instructor: \Href{https://people.mpi-inf.mpg.de/~mseddigh/}{Prof. Masoud Seddighin}}
      {Responsible for designing assignments for some sessions as well as the final test.}{Fall 2021}

    \resumeSubheading
      {Design of Algorithms}{Instructor: \Href{http://sharif.edu/~zarrabi/}{Prof. H. Zarrabi-Zadeh}}
      {Responsible for designing the assignment and TA class on NP-completeness.}{Fall 2022}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Programming Projects}
\resumeSubHeadingListStart


\resumeItem{ChessFX}{Based on MVC architecture, I implemented a graphical chess game using JavaFX. (Jun 2020) [\Href{https://github.com/mahdavifar2002/ChessFX}{link to Github repo}]}

\resumeItem{C-minus Compiler}{In this project, we implemented a simple compiler for a simplified version of the C language, called C-minus. I learned to work with DFAs, the LL parsing method, and code-generation techniques. (Feb 2022) [\Href{https://github.com/AlipourIm/Compiler_Design_And_Implementation_Project}{link to Github repo}]}

\resumeItem{Simple Ray Tracer}{Following Peter Shirley's ``Ray Tracing in One Weekend" book, I implemented my first simple ray tracer. In this project I learned about basics of ray tracing and  antialiasing, implementation of reflections for several materials, depth of field, etc. (Nov 2022) [\Href{https://github.com/mahdavifar2002/ray-tracing-in-one-weekend/}{link to Github repo}]}


\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
